Family of accessibility measures

### 2024-12-30 TRB/TRB-pres.qmd
V1 of the TRB presentation

---
title: "Family of accessibility measures"
format: revealjs
---

@@

## Skip over
(plot of how accessibility research interacts with gravity modelling)

>>>>

---
title: "Family of accessibility measures"
format: revealjs
---
```{r}
library(here)
library(knitr)
library(glue)
```

@@

Plot of how accessibility research (cites Hansen) interacts with gravity modelling (cites Wilson):
```{r}
include_graphics(glue(here(), "/data-raw/Han_Wilson_bib_coupling_plot.png"))
```
